Figures and Tables

### 2021-02-04 paper/figures_tables.Rmd
update with GP tails

@@

ggsave("paper/test.png",
       D,
       width = 6,
       height = 9,
       dpi = 300)

>>>>

```{r, fig.width=6, fig.height=3}
ggplot(data = data.frame(x = c(160, 1000)), aes(x)) +
  stat_function(aes(linetype = "Null"), fun = devd, args = list(scale = null_ci[1,2], shape = null_ci[2,2], type = "GP")) +
  stat_function(aes(linetype = "Individual"), fun = devd, args = list(scale = indiv_ci[1,2], shape = indiv_ci[2,2], type = "GP")) +
  stat_function(aes(linetype = "Family"), fun = devd, args = list(scale = fam_ci[1,2], shape = fam_ci[2,2], type = "GP")) +
  ylab("Density") + xlab("Distance (m)") +
  theme_bw()  +
  theme(legend.position = c(0.7, 0.7),
        legend.title = element_blank())
```

@@

# ggsave("paper/test.png",
#        D,
#        width = 6,
#        height = 9,
#        dpi = 300)

D
